Generative Simplex Mapping: Nonlinear Endmember Extraction and Unmixing for Hyperspectral Imagery

### 2024-07-12 paper/paper.tex
some more minor changes
updated to fit parameter sweep for robot team dye data

\subsection{Nonlinear Mixing: Water Contaminant Identification}
- describe robot team data collection & processing
- describe

@@

- Discuss other applications of the GSM
    - Optimal route planning for in-situ data collection based on prize-collecting travelling salesman problem, i.e. construct a route which maximizies area traversed in GSM latent space (e.g. the n-simplex). 
    - Applications to source apportionment, e.g. linear GSM can be used for standard source apportionment problems

>>>>

\subsection{Nonlinear Mixing: Water Contaminant Identification}
- describe robot team data collection and processing
- describe

@@

- Discuss other applications of the GSM
    - Optimal route planning for in-situ data collection based on prize-collecting travelling salesman problem, i.e. construct a route which maximizies area traversed in GSM latent space (e.g. the n-simplex). 
    - Applications to source apportionment, e.g. linear GSM can be used for standard source apportionment problems (no reactions) and nonlinear GSM may be useful for modeling scenarios with aditional complications due to reactions and transfport from source to receptor.
